Comparing software variability across and within fMRI analysis packages

### 2022-01-03 paper/paper.tex
camille comment results start

\section{Results}
The scripts, Docker images, and data to reproduce the results are available
in our GitHub repository at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

>>>>

\section{Results}
The scripts, Docker images, and data \camille{maybe a detail but consider using something like ``and derived datasets that were used to reproduce the results'' ? As it is now, it made me wonder whether the whole nifti dataset was in the github repo} to reproduce the results are available
in our GitHub repository at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
